My Findings

### 2024-03-20 Findings (Shared Folder)/Chapters/MeetingLog.tex
new notes added
new section for feedbacks

>>>>

\subsection{12 March Meeting}
\begin{itemize}
	\item Things to discuss: going through the qualitative study once again, discussing why we can not have $ \kappa $ directly appearing in the non-dimensionalized version, discussing the effect of $ \kappa $ on the dynamics.

	\item 
	\[ \frac{\partial n}{\partial t} = D \frac{\partial^2 n}{\partial x^2} - \frac{\partial(nv)}{\partial x} + (\lambda_s - \delta_t)n - \kappa_2 n^2. \]
	This can be thought of as a model that $ \lambda_b \to 0 $.
\end{itemize}

\subsection{20 March Meeting}
\begin{itemize}
	\item Jupiter: More analysis on the vertical asymptotic.
	\item Laurent: Drawing a diagram summerizing all of the different interactions happening
	\begin{itemize}
		\item Effect of drug on vasculature
		\item Effect of vasculature on tumor response
		\item Effect of vasculature on drug delivery
		\item what is the topology of the reaction graph?
	\end{itemize}
	\item Jupiter: adaptive systems
	\item Leah:
\end{itemize}
